---
title: "Untitled"
author: "Yihao Li(yl4326)"
date: "2020/1/16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basic Graphing
```{r}
library(ucidata)
library(tidyverse)
library(nullabor)
library(dplyr)
```

Use one of the numeric variables in the `abalone` dataset.
```{r}
head(abalone)  
```

#traditional histogram, for continuous value, aes(variable), remember to define bins = or binwidth =  
```{r}
ggplot(abalone, aes(diameter))+
  geom_histogram(bins = 10)
```

# facet by another variable
```{r}
ggplot(abalone, aes(diameter)) + 
  geom_histogram(bins = 25) + 
  facet_grid("sex")
```

Plot multiple boxplots, grouped by `sex` for the same variable. The boxplots should be ordered by decreasing median from left to right.

```{r,fig.width = 4, fig.height = 4}
library(forcats)
ggplot(abalone, aes(x = fct_reorder(sex, diameter, median, .desc = TRUE), y = diameter))+
  geom_boxplot()+
  xlab("sex")
```

Plot overlapping density curves of the same variable, one curve per factor level of `sex`, on a single set of axes. Each curve should be a different color.

```{r, fig.width = 4, fig.height = 4}
ggplot(abalone, aes(diameter))+
  geom_density(aes(color=sex))
```


a) Use `tidyr::gather()` to convert the numeric columns in the  `glass` dataset in the **ucidata** package to two columns: `variable` and `value`. The first few rows should be:

```
  variable   value
1       RI 1.52101
2       RI 1.51761
3       RI 1.51618
4       RI 1.51766
5       RI 1.51742
6       RI 1.51596
```
```{r}
glass
```
`glass` have the first column removed, select_if it is numeric, gather with category type column `variable` and value column named `value`
```{r}
gatherglass = glass[-1] %>% dplyr::select_if(., is.numeric, ) %>% tidyr::gather(key = "variable", value = "value")
head(gatherglass)
```

Use this form to plot histograms of all of the variables in one plot by faceting on `variable`. 
```{r}
ggplot(gatherglass, aes(value))+
  geom_histogram()+
  facet_wrap("variable", scales = "free")
```

# Unimodal type check normal

1. Draw a normal curve with same mean and std.deviation

```{r}
ggplot(glass, aes(Al))+ 
  geom_histogram(binwidth = 0.1)+ 
  stat_function(fun = function(x, mean, sd, n,bw){
      dnorm(x = x, mean = mean, sd = sd) * n * bw
    },
    args = c(mean = mean(glass$Al), sd = sd(glass$Al), n=nrow(glass), bw = 0.1))
```

2. Shapiro-Wilk test

```{r}
shapiro.test(glass$Al)
```

3. Draw a quantile-quantile (QQ) plot of the variable. 
```{r,fig.width = 4, fig.height = 4}
ggplot(glass, aes(sample = Al)) +
  geom_qq() +
  geom_qq_line()
```

Use the **nullabor** package to create a lineup of histograms in which one panel is the real data and the others are fake data generated from a null hypothesis of normality. Can you pick out the real data? If so, how does the shape of its histogram differ from the others? 

```{r}
al <- glass[c("Al")]
ggplot(lineup(null_dist("Al", "norm"), true = al, pos = 1, n = 9), aes(Al)) +
  geom_histogram() +
  facet_wrap (~.sample)
```

```{r}
fire = forest_fires[c("month", "area", "rain", "wind", "temp")]
fire$month <- factor(fire$month, levels = c("jan","feb","mar","apr","may","jun","jul","aug","sep","oct", "nov", "dec"))
ggplot(fire, aes(area)) +
  geom_histogram() +
  facet_wrap(~month, scale = "free")
```
```{r,fig.width = 5, fig.height = 4}
average <- fire %>% group_by(month) %>% summarize (mean_area = mean(area), mean_temp = mean(temp), mean_wind = mean(wind), mean_rain = mean(rain))
ggplot(average, aes(x = month, y = mean_area)) +
  geom_col()
ggplot(fire, aes(x = fct_reorder(month, area, max, .desc = TRUE), y = area))+
  geom_boxplot()+
  xlab("month")
```

# Horizontal Barchart


(a) Create a horizontal bar chart of the responses to Q20.
```{r}
data = forwards::useR2016

q20_freq <- data %>% 
  group_by(Q20) %>% 
  summarise(freq = n()) %>% 
  mutate(Q20 = ifelse(is.na(Q20), "NA", as.character(Q20)))

ggplot(q20_freq, aes(x=fct_reorder(.f=Q20, .x=freq), y=freq)) + 
  geom_col(color="black", fill="orange") + 
  coord_flip() + 
  labs(x="Medium", y="Count", title="Survey responses: Preferred medium for R community news",
       caption="Dataset: useR2016 \n Package: forwards \nLink:https://cran.r-project.org/web/packages/forwards/forwards.pdf") 
```
(b) Create a vertical bar chart of the responses to Q11.
```{r}
q11_freq <- data %>% 
  group_by(Q11) %>% 
  summarise(freq = n()) %>% 
  mutate(Q11 = ifelse(is.na(Q11), "NA", as.character(Q11)))

q11_freq$Q11 <- factor(q11_freq$Q11, levels = c("< 2 years", "2-5 years", "5-10 years", "> 10 years", "NA"))
  
ggplot(q11_freq, aes(x=Q11, y=freq)) +
  geom_col(color="black", fill="orange") + 
  labs(x="Years", y="Count", title="Survey responses: Duration for which they have been using R",
       caption="Dataset: useR2016 \n Package: forwards \n Link:https://cran.r-project.org/web/packages/forwards/forwards.pdf") 
```

(c) Create a horizontal stacked bar chart showing the proportion of respondents for each level of Q11 who are over 35 vs. 35 or under. Use a descriptive title. 
```{r}
q11_stack <- data[, c("Q11", "Q3")] %>%
  na.omit() %>% 
  group_by(Q11, Q3) %>% 
  count(Q11)


ggplot(q11_stack, aes(fill=Q3, y=n, x=Q11)) +
  geom_bar(position = "fill", stat = "identity") + 
  xlab("usage duration") + 
  ylab("proportion")+
  coord_flip()+
  ggtitle("R usage breakdown with respect to age distribution")
```

(d) Create a horizontal stacked bar chart showing the proportional breakdown of Q11 for each level of Q3, faceted on Q2. Use a descriptive title. 
```{r}
q11_facet <- data[, c("Q11", "Q3", "Q2")] %>% na.omit() %>% group_by(Q11, Q3, Q2) %>% count(Q3)

ggplot(q11_facet, aes(fill=Q11, y=n, x=Q3)) +
  geom_bar(position = "fill", stat = "identity") +
  facet_grid(q11_facet$Q2) +
  xlab("Age Breakdown") + 
  ylab("proportion")+
  guides(fill=guide_legend(title = "R Usage")) +
  coord_flip()+
  ggtitle("R usage breakdown by gender and age group")
```

(e) For the next part, we will need to be able to add line breaks (`\n`) to long tick mark labels. Write a function that takes a character string and a desired approximate line length in number of characters and substitutes a line break for the first space after every multiple of the specified line length.

```{r}
line_breaks <- function(x, n){
split_str <- strsplit(x, "")
split_str <- split_str[[1]]

for (i in 1:length(split_str)){
  if (i%%n == 0){
    while (split_str[i] != " " & i<length(split_str)) {
      i=i+1
    }
    if(split_str[i] == " "){
      split_str[i] = "\n"
    }
  }
}

x_new <- paste(split_str, collapse='')
return(x_new)
}
x <- "We hold these truths to be self-evident, that all men are created equal, that they are endowed by their Creator with certain unalienable Rights, that among these are Life, Liberty and the pursuit of Happiness."

line_breaks(x, 50)
```

(f) Create a horizontal bar chart that shows the percentage of positive responses for `Q13 - Q13_F`. Use your function from part (e) to add line breaks to the responses. Your graph should have one bar each for `Q13 - Q13_F`.
```{r}
  df_f1 = data %>% group_by(Q13) %>% summarize(count = n())%>% mutate(percent = count*100/sum(count)) 
  df_f2 = data %>% group_by(Q13_B) %>% summarize(count = n())%>% mutate(percent = count*100/sum(count))   
  df_f3 = data %>% group_by(Q13_C) %>% summarize(count = n())%>% mutate(percent = count*100/sum(count)) 
  df_f4 = data %>% group_by(Q13_D) %>% summarize(count = n())%>% mutate(percent = count*100/sum(count)) 
  df_f5 = data %>% group_by(Q13_E) %>% summarize(count = n())%>% mutate(percent = count*100/sum(count))   
  df_f6 = data %>% group_by(Q13_F) %>% summarize(count = n())%>% mutate(percent = count*100/sum(count)) 
  result = data_frame(question = c(line_breaks(df_f1$Q13[1],30),
               line_breaks(df_f2$Q13_B[1],30),
               line_breaks(df_f3$Q13_C[1],30),
               line_breaks(df_f4$Q13_D[1],30),
               line_breaks(df_f5$Q13_E[1],30),
               line_breaks(df_f6$Q13_F[1],30)),
         percentage = c(df_f1$percent[1],
               df_f2$percent[1],
               df_f3$percent[1],
               df_f4$percent[1],
               df_f5$percent[1],
               df_f6$percent[1]))
  ggplot(result, aes(x = question, y = percentage))+
    geom_col(color="black", fill="orange")+
    labs(title = "Percentage of positive response by Q")+
    coord_flip()
```

(a) Use the `paths_allowed()` function from **robotstxt** to make sure it's ok to scrape https://www.rottentomatoes.com/browse/box-office/. Then use **rvest** functions to find relative links to individual movies listed on this page. Finally, paste the base URL to each to create a character vector of URLs.
Display the first six lines of the vector.
```{r}
library(rvest)
library(robotstxt)
library(stringi)
```

```{r}
paths_allowed("https://www.rottentomatoes.com/browse/box-office/")

data <- read_html("https://www.rottentomatoes.com/browse/box-office/") %>%
  html_nodes("table") %>%
  .[[3]] %>% 
  html_nodes("tr") %>%
  html_nodes("a") %>%
  html_attr("href")

data <- data[10:length(data)]

links_current <- c() 
for (i in 1:length(data)){
  links_current[i] <- paste("https://www.rottentomatoes.com",data[i], sep='')
}
head(links_current, 6)
```

(b) Write a function to read the content of one page and pull out the title, tomatometer score and audience score of the film. Then iterate over the vector of all movies using `do.call() / rbind() / lapply()` or `dplyr::bind_rows() / purrr::map()` to create a three column data frame (or tibble).

Display the first six lines of your data frame.

(Results will vary depending on when you pull the data.)
 
For help, see this SO post: https://stackoverflow.com/questions/36709184/build-data-frame-from-multiple-rvest-elements


Write your data to file so you don't need to scrape the site each time you need to access it.

```{r}
find_triple = function(address){
  web_data <- read_html(address)
  
  title = web_data %>%
    html_nodes("h1.mop-ratings-wrap__title.mop-ratings-wrap__title--top")%>%
    html_text()
  
  score = web_data %>% 
    html_nodes("h2.mop-ratings-wrap__score")%>%
    html_text("span.mop-ratings-wrap__percentage")%>%
    stri_match_last_regex("[0-9]+%")
  
  return(c(title,score[1],score[2]))
}
aggregate_list<- lapply(links_current, find_triple)
aggregate_df = data.frame(do.call(rbind.data.frame, aggregate_list)) 
names(aggregate_df) = c("Name", "tomatometer_score", "audience_score")

#change the data in df into proper type and format
aggregate_df$Name = as.character(aggregate_df$Name)
for (i in 1:length(aggregate_df$Name)){
  aggregate_df$Name[i] <- line_breaks(aggregate_df$Name[i],40)
}
aggregate_df$tomatometer_score = as.numeric(sub("%", "", aggregate_df$tomatometer_score))
aggregate_df$audience_score = as.numeric(sub("%", "", aggregate_df$audience_score))
write.csv(aggregate_df,file = "current_aggregate_df.csv")
```

(c) Create a Cleveland dot plot of tomatometer scores.

```{r}
aggregate_df = read.csv("current_aggregate_df.csv")

clean_df = aggregate_df[-1] %>% na.omit()

theme_dotplot = theme_bw(16) +
  theme(axis.text.y = element_text(size = rel(.75)),
        axis.ticks.y = element_blank(),
        axis.title.x = element_text(size = rel(.75)),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(size = 0.5),
        panel.grid.minor.x = element_blank())

ggplot(clean_df, aes(x = tomatometer_score, y = fct_reorder(Name, tomatometer_score))) +
  geom_point(color = "blue") + 
  ylab("") +
  ggtitle("The tomatometer score\nof top movies") +
  theme_dotplot
```

(d) Create a Cleveland dot plot of tomatometer *and* audience scores on the same graph, one color for each. Sort by audience score.

```{r}
gathered_df = clean_df %>% tidyr::gather(key = "type", value = "score",-Name) 

ggplot(gathered_df, aes(x = score,
                     y = fct_reorder2(Name, type == "audience_score", score, .desc = FALSE),
                     color = type)) +
         geom_point() +
         ylab("") +
         ggtitle("Scores of top movies") +
         theme(plot.title = element_text(size = 15)) +
         theme_dotplot
```

(e) Run your code again for the weekend of July 5 - July 7, 2019. Use **plotly** to create a scatterplot of audience score vs. tomatometer score with the ability to hover over the point to see the film title.

```{r}
paths_allowed("https://www.rottentomatoes.com/browse/box-office/?rank_id=12&country=us")

data <- read_html("https://www.rottentomatoes.com/browse/box-office/?rank_id=12&country=us") %>%
  html_nodes("table") %>%
  .[[3]] %>% 
  html_nodes("tr") %>%
  html_nodes("a") %>%
  html_attr("href")

data <- data[10:length(data)]

links <- c() 
for (i in 1:length(data)){
  links[i] <- paste("https://www.rottentomatoes.com",data[i], sep='')
}
head(links, 6)

aggregate_list<-lapply(links, find_triple)
aggregate_df = data.frame(do.call(rbind.data.frame, aggregate_list)) 
names(aggregate_df) = c("Name", "tomatometer_score", "audience_score")

#change the data in df into proper type and format
aggregate_df$Name = as.character(aggregate_df$Name)
for (i in 1:length(aggregate_df$Name)){
  aggregate_df$Name[i] <- line_breaks(aggregate_df$Name[i],40)
}
aggregate_df$tomatometer_score = as.numeric(sub("%", "", aggregate_df$tomatometer_score))
aggregate_df$audience_score = as.numeric(sub("%", "", aggregate_df$audience_score))
write.csv(aggregate_df, "aggregate_df_jul.csv")
```

```{r fig.height=20,fig.width=10}
aggregate_df = read.csv("aggregate_df_jul.csv")[-1]

clean_df = aggregate_df %>% na.omit()

ggplot(clean_df, aes(x = tomatometer_score, y = fct_reorder(Name, tomatometer_score))) +
  geom_point(color = "blue") + 
  ylab("") +
  ggtitle("The tomatometer score of top movies(Jul 5 to Jul 7)") +
  theme(plot.title = element_text(size = 15)) +
  theme(text=element_text(size=20))+
  theme_dotplot


gathered_df = clean_df %>% tidyr::gather(key = "type", value = "score",-Name) 

ggplot(gathered_df, aes(x = score,
                     y = fct_reorder2(Name, type == "audience_score", score, .desc = FALSE),
                     color = type)) +
         geom_point() +
         ylab("") +
         ggtitle("Scores of top movies(Jul 5 to Jul 7)") +
         theme(plot.title = element_text(size = 15)) +
         theme(text=element_text(size=20))+
         theme_dotplot
```

```{r}
#library(plotly)
#plot_ly(gathered_df, x = ~score, y = ~Name,
#color = ~type, text = ~Name,
#hoverinfo = 'text') %>%
#add_markers()
```

### 3. Weather

[14 points]

Data: `weather` dataset in **nycflights13** package (available on CRAN)


For parts (a) - (d) draw four plots of `wind_dir` vs. `humid` as indicated. For all, adjust parameters to the levels that provide the best views of the data.

(a) Points with alpha blending

```{r}
library(nycflights13)
ggplot(weather, aes(x = humid, y = wind_dir)) +
  geom_point(alpha = 0.2, stroke = 0)
```

(b) Points with alpha blending + density estimate contour lines

```{r}
library(MASS)
ggplot(weather, aes(x = humid, y = wind_dir)) +
  geom_point(alpha = 0.2, stroke = 0)+
  geom_density_2d()
```

(c) Hexagonal heatmap of bin counts

```{r}
library(hexbin)
ggplot(weather, aes(x = humid, y = wind_dir)) +
  scale_fill_viridis_c()+
  geom_hex()
```

(d) Square heatmap of bin counts

```{r}
ggplot(weather, aes(x = humid, y = wind_dir)) +
  scale_fill_viridis_c()+
  geom_bin2d(binwidth=c(5,25))
```

(e) Describe noteworthy features of the data, using the "Movie ratings" example on page 82 (last page of Section 5.3) as a guide. 

There's several "heated bin" i.e. there's high frequency of record fell into these 4 peaks. (Add more)

- There are majorly two peaks in the data, i.e., high density points:
  one at around (humid=40, wind_dir=300)
  and the other one around (humid=, wind_dir=)

- A high density region is present around wind_dir=25 and humid from 50 to 90.

- Density of data is relatively less below humid=25

- There is a relatively low density region between the high density peak and high denisty region:
    from wind_dir (100 to 150) and humid (25 to 100)

(f) Draw a scatterplot of `humid` vs. `temp`. Why does the plot have diagonal lines?

```{r}
ggplot(weather, aes(x = temp, y = humid)) +
  geom_point(alpha = 0.2)
```

The diagonal pattern is because of 

(g) Draw a scatterplot matrix of the continuous variables in the `weather` dataset. Which pairs of variables are strongly positively associated and which are strongly negatively associated?

```{r}
library(ggplot2movies) # data
cont_data = weather %>% dplyr::select(temp, dewp, humid, wind_speed, pressure)
plot(cont_data)
```

strong positive correlation: temperature and dewpoint
strong negative correlation: None

(h) Color the points by `origin`.  Do any new patterns emerge?
```{r}
library(GGally)
library(lattice)
cont_data = weather %>% dplyr::select(origin, temp, dewp, humid, wind_speed, pressure)

pm <- ggpairs(
 cont_data[, 2:6],
 mapping = ggplot2::aes(color = cont_data$origin, alpha = 0.1),
 upper = list(continuous = wrap("density", alpha = 0.6), combo = "box_no_facet"),
 lower = list(continuous = wrap("points", alpha = 0.1,size = 0.05), 
              combo = wrap("dot_no_facet", alpha = 0.1,size = 0.05)),
 legend = 1
)
pm
```